---
title: "ANCOVA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Rmcorr and ANCOVA

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
# Rmcorr and ANCOVA
library(rmcorr)
library(dplyr)


# Import datasets
setwd("~/Desktop/PythonWorkspace/AppInvestigation/Datasets")
group_4_raw <- read.csv('group_4.csv')
group_3_raw <- read.csv('group_3.csv')
group_2_raw <- read.csv('group_2.csv')

# Data format for the analysis
# Drop unused columns
group_4_raw <- select(group_4_raw, -c("Probanden_ID__lfdn", "V2", "V17_2_Interview", "V17_3_Interview",
                                      "V17_4_Interview", "V18_2_Interview", "V18_3_Interview", "V18_4_Interview"))
group_3_raw <- select(group_3_raw, -c("Probanden_ID__lfdn", "V2", "V17_2_Interview", "V17_3_Interview",
                                      "V17_4_Interview", "V18_2_Interview", "V18_3_Interview", "V18_4_Interview"))
group_2_raw <- select(group_2_raw, -c("Probanden_ID__lfdn", "V2", "V17_2_Interview", "V17_3_Interview",
                                      "V17_4_Interview", "V18_2_Interview", "V18_3_Interview", "V18_4_Interview"))

# replicate all participants 4 times
Participant <- group_4_raw["Probanden_ID__lfdn__AppNr"]
Participant <- Participant[rep(seq_len(nrow(Participant)), 4), ]

# Insert Interview's number
Trial <- c(rep(1, nrow(group_4_raw)), rep(2, nrow(group_4_raw)), 
           rep(3, nrow(group_4_raw)), rep(4, nrow(group_4_raw)))

# Append variable from each interview one after another
V4 <- c(group_4_raw["V4_1_Interview"][,], group_4_raw["V4_2_Interview"][,],
        group_4_raw["V4_3_Interview"][,], group_4_raw["V4_4_Interview"][,])

V6 <- c(group_4_raw["V6_1_Interview"][,], group_4_raw["V6_2_Interview"][,],
        group_4_raw["V6_3_Interview"][,], group_4_raw["V6_4_Interview"][,])

V12 <- c(group_4_raw["V12_1_Interview"][,], group_4_raw["V12_2_Interview"][,],
         group_4_raw["V12_3_Interview"][,], group_4_raw["V12_4_Interview"][,])

# group 4 final dataset
group_4 <- data.frame(Participant, Trial, V4, V6, V12)


# replicate all participants 3 times
Participant <- group_3_raw["Probanden_ID__lfdn__AppNr"]
Participant <- Participant[rep(seq_len(nrow(Participant)), 3), ]

# Insert Interview's number
Trial <- c(rep(1, nrow(group_3_raw)), rep(2, nrow(group_3_raw)), 
           rep(3, nrow(group_3_raw)))

# Append variable from each interview one after another
V4 <- c(group_3_raw["V4_1_Interview"][,], group_3_raw["V4_2_Interview"][,],
        group_3_raw["V4_3_Interview"][,])

V6 <- c(group_3_raw["V6_1_Interview"][,], group_3_raw["V6_2_Interview"][,],
        group_3_raw["V6_3_Interview"][,])

V12 <- c(group_3_raw["V12_1_Interview"][,], group_3_raw["V12_2_Interview"][,],
         group_3_raw["V12_3_Interview"][,])

# group 3 final dataset
group_3 <- data.frame(Participant, Trial, V4, V6, V12)


# replicate all participants 2 times
Participant <- group_2_raw["Probanden_ID__lfdn__AppNr"]
Participant <- Participant[rep(seq_len(nrow(Participant)), 2), ]

# Insert Interview's number
Trial <- c(rep(1, nrow(group_2_raw)), rep(2, nrow(group_2_raw)))

# Append variable from each interview one after another
V4 <- c(group_2_raw["V4_1_Interview"][,], group_2_raw["V4_2_Interview"][,])

V6 <- c(group_2_raw["V6_1_Interview"][,], group_2_raw["V6_2_Interview"][,])

V12 <- c(group_2_raw["V12_1_Interview"][,], group_2_raw["V12_2_Interview"][,])

# group 2 final dataset
group_2 <- data.frame(Participant, Trial, V4, V6, V12)
```


## V4 vs V6 group 4

### Sample observations for plotting
RMCORR: assesses the intra-individual or longitudinal change.
To be able to plot, we sample randomly roughly 10 people from the dataset.

```{r group_4_sample_V6_v4}
# set seed to make the sampling reproducible
set.seed(123)
group_4_ind <- sample(seq_len(nrow(group_4)), size = 10)
group_4_sample <- group_4[group_4$Participant %in% group_4[group_4_ind,1],]

V6_V4_sample.rmc <- rmcorr(Participant, V6, V4, group_4_sample)
print(V6_V4_sample.rmc)
```

```{r group_4_sample_plot_V6_V4}
plot(V6_V4_sample.rmc, overall = T, lty=2, xlab = 'V6', ylab = 'V4')
```


**COMMENT:**
r = -0.3968902 and p-value = 0.02705829, there is a negative significant relationship between V6 and V4 intra-individuals, which is weaker than the relationship calculated with the regression line (gray line).  

### All group 4 observations output
```{r group_4_V6_V4}
# Overall rmcorr output
rmc.out <- rmcorr(Participant, V4, V6, group_4)
print(rmc.out)
```

**COMMENT**:
Small effect sizes for rmcorr (r = -0.15) may be caused by heterogenous slopes
(poor model fit), or by consistently near-zero slopes across subjects, or by
restriction in the range of one or both measures.

## V4 vs V12 group 4
### Sample observations for plotting
```{r group_4_sample_V12_V4}
V12_V4_sample.rmc <- rmcorr(Participant, V12, V4, group_4_sample)
print(V12_V4_sample.rmc)
```
```{r group_4_sample_plot_V12_V4}
plot(V12_V4_sample.rmc, overall = T, lty=2, xlab = 'V12', ylab = 'V4')
```


**COMMENT:**
r = -0.37 and p-value = 0.03, there is a negative significant relationship between V6 and V4 intra-individuals, which is weaker than the relationship calculated with the regression line (gray line).  

### All group 4 observations output
```{r group_4_V12_V4}
# Overall rmcorr output
rmc.out <- rmcorr(Participant, V4, V12, group_4)
print(rmc.out)
```

**COMMENT**:
Small effect sizes for rmcorr (r = -0.20).
Observations do not change much across interviews. 

## V4 vs V6 group 3
### Sample observations for plotting
```{r group_3_sample_V6_v4}
# set seed to make the sampling reproducible
set.seed(123)
group_3_ind <- sample(seq_len(nrow(group_3)), size = 10)
group_3_sample <- group_3[group_3$Participant %in% group_3[group_3_ind,1],]

V6_V4_sample.rmc <- rmcorr(Participant, V6, V4, group_3_sample)
print(V6_V4_sample.rmc)
```

```{r group_3_sample_plot_V6_V4}
plot(V6_V4_sample.rmc, overall = T, lty=2, xlab = 'V6', ylab = 'V4')
```


**COMMENT**:
Small effect sizes for rmcorr (r = -0.25) and p=0.27 not statistically significant.

### All group 3 observations output
```{r group_3_V6_V4}
# Overall rmcorr output
rmc.out <- rmcorr(Participant, V4, V6, group_3)
print(rmc.out)
```

## V4 vs V12 group 3
### Sample observations for plotting

```{r group_3_sample_V12_v4}
# set seed to make the sampling reproducible
V12_V4_sample.rmc <- rmcorr(Participant, V12, V4, group_3_sample)
print(V12_V4_sample.rmc)
```
```{r group_3_sample_plot_V12_V4}
plot(V12_V4_sample.rmc, overall = T, lty=2, xlab = 'V6', ylab = 'V4')
```

### All group 3 observations output
```{r group_3_V12_V4}
# Overall rmcorr output
rmc.out <- rmcorr(Participant, V4, V12, group_3)
print(rmc.out)
```

## V4 vs V6 group 2
### Sample observations for plotting
```{r group_2_sample_V6_v4}
# set seed to make the sampling reproducible
set.seed(123)
group_2_ind <- sample(seq_len(nrow(group_2)), size = 10)
group_2_sample <- group_2[group_2$Participant %in% group_2[group_2_ind,1],]

V6_V4_sample.rmc <- rmcorr(Participant, V6, V4, group_2_sample)
print(V6_V4_sample.rmc)
```

```{r group_2_sample_plot_V6_V4}
plot(V6_V4_sample.rmc, overall = T, lty=2, xlab = 'V6', ylab = 'V4')
```

**COMMENT**:
Not statistically significant.

### All group 2 observations output
```{r group_2_V6_V4}
# Overall rmcorr output
rmc.out <- rmcorr(Participant, V4, V6, group_2)
print(rmc.out)
```

## V4 vs V12 group 2
### Sample observations for plotting

```{r group_2_sample_V12_V4}
V12_V4_sample.rmc <- rmcorr(Participant, V12, V4, group_2_sample)
print(V12_V4_sample.rmc)
```
```{r group_2_sample_plot_V12_V4}
plot(V12_V4_sample.rmc, overall = T, lty=2, xlab = 'V6', ylab = 'V4')
```

### All group 3 observations output
```{r group_2_V12_V4}
# Overall rmcorr output
rmc.out <- rmcorr(Participant, V4, V12, group_2)
print(rmc.out)
```
















